Fast Random Integer Generation in an Interval

### 2023-12-02 Paper/main.tex
restructure report a bit
...

Since we can map every integer in an interval $[a,b)$ to the interval $[0,b - a)$ by subtracting $a$, our goal is to generate a uniform random integer in an interval $[0,s)$ for a given $s$.
If we map all integers $x$ in $[0,2^W)$ with the function $x \Mod s$, we get the following sequence:
{\Large
\[
    \overbrace{\underbrace{\overbrace{0,1,\ldots,s - 1}^{\text{$s$ values}},\overbrace{0,1,\ldots,s - 1}^{\text{$s$ values}},\ldots,\overbrace{0,1,\ldots,s - 1}^{\text{$s$ values}}}_{\text{$\left(2^W \div s\right) \cdot s$ values}},\underbrace{0,1,\ldots,\left(2^W \Mod s\right) - 1}_{\text{$2^W \Mod s$ values}}}^{\text{$2^W$ values}}
\]
}%
This motivates the following lemma:
\begin{lemma}[Remainder Multiples]
    For given integers $a,b,s > 0$ with $a < b$, there exist exactly $(b - a) \div s$ integers $x \in [a,b)$ for every $0 \leq r < s$ such that $x \Mod s \equiv r$ whenever $s$ divides $b - a$.
\end{lemma}

@@

\subsection{Structure}
We present and analyse existing techniques for uniformly sampling random integers in an interval $[0,s)$ in \hyperref[sec:2]{Section 2}.
In \hyperref[sec:3]{Section 3}, we present the main contribution of this paper: a nearly-divisionless algorithm to sampler uniform random integers in an interval $[0,s)$.
In \hyperref[sec:4]{Section 4}, we benchmark this new technique in two experiments - shuffling and performance in the novel \textsc{Upmem-Pim} architecture - and \hyperref[sec:5]{Section 5} contains a summary of all results.

@@

@@

@@

%%%%% Experiments
\section{Experiments}\label{sec:4}
\subsection{Shuffling-Experiments}

\subsection{In-Memory-Processing-Experiments}

%%%%% Conclusion
\section{Conclusion}\label{sec:5}

>>>>

Since we can map every integer in an interval $[a,b)$ to the interval $[0,b - a)$ by subtracting $a$, we want to generate a uniform random integer in an interval $[0,s)$ for a given $s$.
If we map all integers $x$ in $[0,2^W)$ with the function $x \Mod s$, we get the following sequence:
{\Large
\[
    \overbrace{\underbrace{\overbrace{0,1,\ldots,s - 1}^{\text{$s$ values}},\overbrace{0,1,\ldots,s - 1}^{\text{$s$ values}},\ldots,\overbrace{0,1,\ldots,s - 1}^{\text{$s$ values}}}_{\text{$\left(2^W \div s\right) \cdot s$ values}},\underbrace{0,1,\ldots,\left(2^W \Mod s\right) - 1}_{\text{$2^W \Mod s$ values}}}^{\text{$2^W$ values}}
\]
}%
This motivates the following lemma:
\begin{lemma}[Remainder Multiples]
    For given integers $a,b,s > 0$ with $a < b$, there exist exactly $(b - a) \div s$ integers $x \in [a,b)$ for every $0 \leq r < s$ such that $x \Mod s \equiv r$ whenever $s$ divides $b - a$.
\end{lemma}

@@

\subsection{Structure}
We present and analyse existing techniques for uniformly sampling random integers in an interval $[0,s)$ in \hyperref[sec:2]{Section 2}.
In \hyperref[sec:3]{Section 3}, we present the main contribution of this paper: a nearly-divisionless algorithm to sampler uniform random integers in an interval $[0,s)$.
In \hyperref[sec:4]{Section 4}, we provide a short summary.

@@

\subsubsection{Modulo Reduction}

\subsubsection{Multiply-and-Shift}

\subsubsection{Floating-Point Conversion}

@@

\subsubsection{OpenBSD}

\subsubsection{Java}

\subsubsection{Fast-Dice-Roller}

\subsubsection{Bitmask}

@@

%%%%% Conclusion
\section{Conclusion}\label{sec:4}
